---
title: "Dedifferentiation and Adaptation Figures"
author: "Jonathan Nelson and Annie Lackey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
    number_sections: yes
    theme: bootstrap
    df_print: paged
    code_folding: hide
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
if (!require("Seurat")) {install.packages("Seurat"); require("Seurat")}
if (!require("patchwork")) {install.packages("patchwork"); require("patchwork")}
if (!require("knitr")) {install.packages("knitr"); require("knitr")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("BiocManager")) {install.packages("BiocManager"); require("BiocManager")}
if (!require("tibble")) {install.packages("tibble"); require("tibble")}
if (!require("ggpmisc")) {install.packages("ggpmisc"); require("ggpmisc")}
if (!require("RColorBrewer")) {install.packages("RColorBrewer"); require("RColorBrewer")} #color
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")}
if (!require("DESeq2")) {BiocManager::install('DESeq2'); require("DESeq2")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("stringr")) {install.packages("stringr"); require("stringr")}
if (!require("car")) {install.packages("car"); require("car")}
if (!require("openxlsx")) {install.packages("openxlsx"); require("openxlsx")}
if (!require("readxl")) {install.packages("readxl"); require("readxl")}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggvenn")) {install.packages("ggvenn"); require("ggvenn")}
if (!require("kableExtra")) {install.packages("kableExtra"); require("kableExtra")} # for color brewer
if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
if (!require("tidyr")) {install.packages("tidyr"); require("tidyr")}
if (!require("clusterProfiler")) {BiocManager::install('clusterProfiler'); require("clusterProfiler")}
if (!require("enrichplot")) {BiocManager::install('enrichplot'); require("enrichplot")}
if (!require("gplots")) {install.packages("gplots"); require("gplots")}
if (!require("geneName")) {install.packages("geneName"); require("geneName")}




```


# Load Datasets

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}
rm(list = ls())

All <- readRDS(here("Output", "All_integrated_Unique_Scores2.rds"))

load(here("Code", "Dedifferentiation_merged_df2.RData"))

```

## Selecting Color Scheme

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

display.brewer.pal(9, "Dark2")
brewer.pal(9, "Dark2")


Dediff.color <- c("#1B9E77", "#D95F02", "#7570B3")

Adapt.color <- c("#66A61E","#E6AB02","#E7298A")

```

# Dedifferentation Score

## CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

merged_df <- merged_df_cacpr

df2x <- merged_df %>%
  group_by(subclass.All, class.sample.df1a, Dedifferentiation ) %>%
  summarize(Count = n())

# summarize as a percentage of the total number of cells in each subclass.All

df2x <- df2x %>%
  group_by(subclass.All, class.sample.df1a) %>%
  mutate(Percentage = Count / sum(Count) * 100)

df2x <- df2x %>%
  filter(!grepl("PTinj", subclass.All))

df_cacpr <- df2x %>%
  filter(class.sample.df1a == "CACPR")

df_cacpr_sham <- df2x %>%
 filter(class.sample.df1a == "CACPR Sham")

```


### Sham Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_cacpr_sham, aes(x = subclass.All, y = Count, fill = Dedifferentiation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Dediff.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### CACPR Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_cacpr, aes(x = subclass.All, y = Count, fill = Dedifferentiation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Dediff.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### UMAP

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

SO2 <- subset(All, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)

head(SO2@meta.data)

Idents(SO2) <- SO2@meta.data$subclass.All

SO2 <- subset(SO2, idents = c("PTinj"), invert = TRUE)

Idents(SO2) <- SO2@meta.data$class.sample

SO2 <- subset(SO2, idents = c("CACPR Sham", "CACPR"))

DimPlot(SO2, group.by = "Dedifferentiation", split.by = "class.sample", cols = Dediff.color) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none") 

```

## IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

merged_df <- merged_df_iri

df2x <- merged_df %>%
  group_by(subclass.All, class.sample.df1a, Dedifferentiation ) %>%
  summarize(Count = n())

# summarize as a percentage of the total number of cells in each subclass.All

df2x <- df2x %>%
  group_by(subclass.All, class.sample.df1a) %>%
  mutate(Percentage = Count / sum(Count) * 100)

df2x <- df2x %>%
  filter(!grepl("PTinj", subclass.All))

df_iri <- df2x %>%
  filter(class.sample.df1a == "IRI")

df_iri_sham <- df2x %>%
 filter(class.sample.df1a == "IRI Sham")

```

### Sham Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_iri_sham, aes(x = subclass.All, y = Count, fill = Dedifferentiation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Dediff.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### IRI Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_iri, aes(x = subclass.All, y = Count, fill = Dedifferentiation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Dediff.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### UMAP

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

SO2 <- subset(All, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)

head(SO2@meta.data)

Idents(SO2) <- SO2@meta.data$subclass.All

SO2 <- subset(SO2, idents = c("PTinj"), invert = TRUE)

Idents(SO2) <- SO2@meta.data$class.sample

SO2 <- subset(SO2, idents = c("IRI Sham", "IRI"))

DimPlot(SO2, group.by = "Dedifferentiation", split.by = "class.sample", cols = Dediff.color) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none") 

```

# Adaptation Score

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

load(here("Code", "Adaptation_merged_df2.RData"))

```

## CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

merged_df <- merged_df_cacpr

df2x <- merged_df %>%
  group_by(subclass.All, class.sample.df1a, Adaptation ) %>%
  summarize(Count = n())

# summarize as a percentage of the total number of cells in each subclass.All

df2x <- df2x %>%
  group_by(subclass.All, class.sample.df1a) %>%
  mutate(Percentage = Count / sum(Count) * 100)

df2x <- df2x %>%
  filter(!grepl("PTinj", subclass.All))

df_cacpr <- df2x %>%
  filter(class.sample.df1a == "CACPR")

df_cacpr_sham <- df2x %>%
 filter(class.sample.df1a == "CACPR Sham")

```


### Sham Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_cacpr_sham, aes(x = subclass.All, y = Count, fill = Adaptation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Adapt.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### CACPR Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_cacpr, aes(x = subclass.All, y = Count, fill = Adaptation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Adapt.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### UMAP

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

SO2 <- subset(All, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)

head(SO2@meta.data)

Idents(SO2) <- SO2@meta.data$subclass.All

SO2 <- subset(SO2, idents = c("PTinj"), invert = TRUE)

Idents(SO2) <- SO2@meta.data$class.sample

SO2 <- subset(SO2, idents = c("CACPR Sham", "CACPR"))

DimPlot(SO2, group.by = "Adaptation", split.by = "class.sample", cols = Adapt.color) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none") 

```

## IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

merged_df <- merged_df_iri

df2x <- merged_df %>%
  group_by(subclass.All, class.sample.df1a, Adaptation ) %>%
  summarize(Count = n())

# summarize as a percentage of the total number of cells in each subclass.All

df2x <- df2x %>%
  group_by(subclass.All, class.sample.df1a) %>%
  mutate(Percentage = Count / sum(Count) * 100)

df2x <- df2x %>%
  filter(!grepl("PTinj", subclass.All))

df_iri <- df2x %>%
  filter(class.sample.df1a == "IRI")

df_iri_sham <- df2x %>%
 filter(class.sample.df1a == "IRI Sham")

```

### Sham Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_iri_sham, aes(x = subclass.All, y = Count, fill = Adaptation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Adapt.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### IRI Bargraph

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

ggplot(df_iri, aes(x = subclass.All, y = Count, fill = Adaptation)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        axis.text.y = element_text(colour = "black"),
        axis.ticks = element_line(size = 1)) +
    scale_fill_manual(values = Adapt.color) +
  xlab("") +
  ylab("Percentage of cells") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)))

```

### UMAP

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

SO2 <- subset(All, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)

head(SO2@meta.data)

Idents(SO2) <- SO2@meta.data$subclass.All

SO2 <- subset(SO2, idents = c("PTinj"), invert = TRUE)

Idents(SO2) <- SO2@meta.data$class.sample

SO2 <- subset(SO2, idents = c("IRI Sham", "IRI"))

DimPlot(SO2, group.by = "Adaptation", split.by = "class.sample", cols = Adapt.color) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none") 

```
# Correlating with Sodium Pump

## Correlating with Atp1a1

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=14, fig.height=6}


custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

All <- readRDS(here("Output", "All_integrated.rds"))

All@meta.data$class.sample <- factor(All@meta.data$class.sample, levels = c("CACPR Sham", "CACPR", "IRI Sham", "IRI"))

Idents(All) <- All@meta.data$class.sample
All

All2 <- subset(All, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)
All2 


Idents(All) <- All@meta.data$subclass.All

Idents(All) <- All@meta.data$class.sample

VlnPlot(All, "Atp1a1", group.by = "subclass.All", split.by = "class.sample", idents = c("CACPR Sham", "CACPR"), pt.size = 0.1) +
  theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    ) +
  ylab("Expression of Atp1a1") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("Expression of Atp1a1 at Baseline and After CA/CPR")



```

## Correlation Plot

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=14, fig.height=6}

load(here("Code","merged_df_norm_delta_cacpr_final_1.RData"))

```


#### Run correlation test

##### Dedifferentiation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width= 20, fig.align = 'center'}

# dediff
cor_result_dediff_cacpr <- cor.test(merged_df_norm_delta_cacpr_final_1$norm_delta_Atp1a1, merged_df_norm_delta_cacpr_final_1$Percent_Dediff, method = "spearman")
cor_result_dediff_cacpr
```

#### Visualize correlation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width= 15, fig.height = 8, fig.align = 'center'}

#dediff
corr_coeff_d_cacpr <- cor_result_dediff_cacpr$estimate
corr_pvalue_d_cacpr <- cor_result_dediff_cacpr$p.value

ggplot(merged_df_norm_delta_cacpr_final_1, aes(x = norm_delta_Atp1a1, y = Percent_Dediff)) +
  geom_point(size = 5) +
  theme_classic() +
  theme(axis.line = element_line(size = 2, colour = "black"),
        text = element_text(size=30)) +
   labs(
    x = "Normalized Change in Atp1a1 expression",
    y = "High and Medium Dedifferentiation",
    title = ""
  ) +
    geom_text_repel(aes(label = subclass.All), vjust = -0.5, size = 7)

```

### Atp1b1

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width= 15, fig.height = 8, fig.align = 'center'}

VlnPlot(All, "Atp1b1", group.by = "subclass.All", split.by = "class.sample", idents = c("CACPR Sham", "CACPR"), pt.size = 0.1) +
  theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    ) +
  ylab("Expression of Atp1a1") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("Expression of Atp1b1 at Baseline and After CA/CPR")

```


#### Run correlation test

##### Dedifferentiation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width= 20, fig.align = 'center'}

# dediff
cor_result_dediff_cacpr_2 <- cor.test(merged_df_norm_delta_cacpr_final_1$norm_delta_Atp1b1, merged_df_norm_delta_cacpr_final_1$Percent_Dediff, method = "spearman")
cor_result_dediff_cacpr_2
```

#### Visualize correlation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width= 15, fig.height = 8, fig.align = 'center'}

#dediff
corr_coeff_d_cacpr_1b1 <- cor_result_dediff_cacpr_2$estimate
corr_pvalue_d_cacpr_1b1 <- cor_result_dediff_cacpr_2$p.value

ggplot(merged_df_norm_delta_cacpr_final_1, aes(x = norm_delta_Atp1b1, y = Percent_Dediff)) +
  geom_point(size = 5) +
  theme_classic() +
  theme(axis.line = element_line(size = 2, colour = "black"),
        text = element_text(size=30)) +
   labs(
    x = "Normalized Change in Atp1b1 expression",
    y = "High and Medium Dedifferentiation",
    title = ""
  ) +
    geom_text_repel(aes(label = subclass.All), vjust = -0.5, size = 7)
```


# Session Info

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

sessionInfo()

```


  