---
title: "Figure 2 and 3"
author: "Jonathan Nelson and Annie Lackey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
    number_sections: yes
    theme: bootstrap
    df_print: paged
    code_folding: hide
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
if (!require("Seurat")) {install.packages("Seurat"); require("Seurat")}
if (!require("patchwork")) {install.packages("patchwork"); require("patchwork")}
if (!require("knitr")) {install.packages("knitr"); require("knitr")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("BiocManager")) {install.packages("BiocManager"); require("BiocManager")}
if (!require("tibble")) {install.packages("tibble"); require("tibble")}
if (!require("ggpmisc")) {install.packages("ggpmisc"); require("ggpmisc")}
if (!require("RColorBrewer")) {install.packages("RColorBrewer"); require("RColorBrewer")} #color
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")}
if (!require("DESeq2")) {BiocManager::install('DESeq2'); require("DESeq2")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("stringr")) {install.packages("stringr"); require("stringr")}
if (!require("car")) {install.packages("car"); require("car")}
if (!require("openxlsx")) {install.packages("openxlsx"); require("openxlsx")}
if (!require("readxl")) {install.packages("readxl"); require("readxl")}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggvenn")) {install.packages("ggvenn"); require("ggvenn")}
if (!require("kableExtra")) {install.packages("kableExtra"); require("kableExtra")} # for color brewer
if (!require("gplots")) {install.packages("gplots"); require("gplots")} # for color brewer

```


# Load CACPR Dataset

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}
rm(list = ls())

CACPR <- readRDS(here("Output", "CACPR_integrated.rds"))
DefaultAssay(CACPR) <- "RNA"

head(CACPR@meta.data)

Idents(CACPR) <- CACPR@meta.data$subclass.CACPR

DimPlot(CACPR, reduction = "umap")

DimPlot(CACPR, group.by = "class.sample", cols = c("#4974A5", "#B81316"))

DimPlot(CACPR, split.by = "class.sample", label = TRUE)

table(Idents(CACPR))
prop.table(table(Idents(CACPR)))

SO <- CACPR

SO@meta.data$subclass.CACPR <- factor(SO@meta.data$subclass.CACPR, levels = c("PTS1", "PTS2", "PTS3", "PTinj", "DTL", "TAL1", "TAL2", "MD", "DCT1", "DCT2", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "MES", "CONTRACT", "PODO", "EC", "LYMPH", "MACRO", "LYMPHO"))

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "CACPR"))

SO@meta.data <- SO@meta.data %>% 
  mutate(class.Names = case_when(
     Sample == "MH1" ~ "CACPR",
     Sample == "MH3" ~ "Sham",
))

SO@meta.data$class.Names <- factor(SO@meta.data$class.Names, levels = c("Sham", "CACPR"))



```

# Set the color palette

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=12, fig.height=8}

custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

```


# Fig 2

## Fig 2a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=12, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1) + ggtitle(NULL) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))

```



## Fig 2b 

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=10}

markers.to.plot1 <- c("Lrp2",         # PT
                      "Slc5a12",      # PT-S1
                      "Slc13a3",      # PT-S2
                      "Slc16a9",      # PT-S3
                      "Havcr1",       # Injured PT
                      "Epha7",        # dTL
                      "Slc12a1",      # TAL
                      "Cldn10",       # TAL
                      "Cldn16",       # TAL
                      "Nos1",         # MD
                      "Slc12a3",      # DCT
                      "Pvalb",        # DCT1
                      "Slc8a1",       # DCT2, CNT
                      "Aqp2",         # PC
                      "Slc4a1",       # IC-A
                      "Slc26a4",      # IC-B
                      "Upk1b",        # Uro
                      "Ncam1",        # PEC
                      "Pdgfrb",       # Perivascular
                      "Piezo2",       # Mesangial
                      "Pdgfra",       # Fib
                      "Acta2",        # Mural
                      "Nphs1",        # Podo
                      "Kdr",          # Capillary Endo
                      "Lyve1",        # Lymph
                      "Ptprc",        # Immune
                      "Cd74",         # Macrophage
                      "Skap1"         # B/T Cells 
                      )


DotPlot(SO,
features = markers.to.plot1,
dot.scale = 8,
dot.min = 0,
scale.max = 100,
scale.min = 0,
col.min = -2.5,
col.max = 2.5) +
  coord_flip() +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab(NULL) +
  ylab(NULL)


```

# Supplemental Fig 1

## Fig S1a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO, features = "nFeature_RNA", split.by = "class.sample", group.by = "class.lab", pt.size = 0.1) +
  theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  ylab("Number of Genes Detected") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("nFeature RNA")

```

## Fig S1b

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO, "nCount_RNA", split.by = "class.sample", group.by = "class.lab", pt.size = 0.1) +
    theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  ylab("Number of mRNA Molecules Detected") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("nCount RNA")



table(SO@meta.data$class.sample)

df <- FetchData(object = SO, vars = c("class.sample", "nFeature_RNA", "nCount_RNA"), layer = "counts")

df2 <- df %>%
  group_by(class.sample) %>%
  summarize(
    Count = n(),
    "Median nFeature_RNA" = median(nFeature_RNA, na.rm = TRUE),
    "Median nCount_RNA" = median(nCount_RNA, na.rm = TRUE)
  )

df2



```
## Fig S2c


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=12, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1, label = TRUE, label.size = 6, repel = TRUE) + ggtitle(NULL) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))

```



```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=30, fig.height=20}

f5 <- FeaturePlot(SO,
             features = markers.to.plot1,
             cols = c("lightgrey", "royal blue"),
             combine = F, 
             order = T) 

for(i in 1:length(f5)) {
  f5[[i]] <- f5[[i]] & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))
}

cowplot::plot_grid(plotlist = f5)

```

## Fig 2c

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1, group.by = "class.Names", cols = c("#4974A5","#B81316")) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))

```



## Fig 2d

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=8}

DimPlot(SO, reduction = "umap", split.by = "class.Names", pt.size = 1) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```


## Fig 2f

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=8}

FeaturePlot(SO, "Havcr1", split.by = "class.Names", pt.size = 1, order = TRUE) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none") 


```

## Fig 2g

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE,  fig.width=6, fig.height=6}

Idents(SO) <- "class.CACPR"

VlnPlot(SO, features = "Havcr1", idents = "PT", group.by = "class.CACPR", split.by = "class.Names", cols = c("#4974A5","#B81316")) +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
        axis.text.x = element_blank()
      ) + xlab("") 

```

# Supplemental Fig 2

## Proportion by "subclass"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

t1 <- table(SO@meta.data$subclass.CACPR, SO@meta.data$class.Names)[, c("Sham", "CACPR")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

## Proportion by "class"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

t1 <- table(SO@meta.data$class.CACPR, SO@meta.data$class.Names)[, c("Sham", "CACPR")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

## Proportion by "type"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

t1 <- table(SO@meta.data$type.CACPR, SO@meta.data$class.Names)[, c("Sham", "CACPR")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

# Fig 3

## Fig 3a

### Cluster DEGs for CACPR Dataset

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

rm(list = ls())

load(here("Output", "CACPR_Only_Subclass_Condition_DEGs.RData"))

# List the objects in the environment
  objects_in_environment <- ls()

data_frames <- Filter(is.data.frame, mget(ls()))

# Initialize an empty data frame to store the results
output_table <- data.frame(Data_Frame = character(),
                           Number_of_Obs = numeric(),
                           Number_of_Positive_Log2FC = numeric(),
                           Number_of_Negative_Log2FC = numeric(),
                           stringsAsFactors = FALSE)

# Loop through each data frame
for (df_name in names(data_frames)) {
  df <- data_frames[[df_name]]
  
  # Get the number of observations in the data frame
  num_obs <- nrow(df)
  
  # Count the number of observations with positive log2FC
  positive_count <- sum(df$avg_log2FC > 0)
  
  # Count the number of observations with negative log2FC
  negative_count <- sum(df$avg_log2FC < 0)
  
  # Create a row in the output table
  output_row <- data.frame(Data_Frame = df_name,
                           Number_of_Obs = num_obs,
                           Number_of_Positive_Log2FC = positive_count,
                           Number_of_Negative_Log2FC = negative_count,
                           stringsAsFactors = FALSE)
  
  # Append the row to the output table
  output_table <- rbind(output_table, output_row)
}

# Print the output table
output_table

```

### Print Graph of DEGs

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=6, fig.width=10}

# Measure the total number of DEGs (sum of output_table$Number_of_Obs)
v1 <-sum(output_table$Number_of_Obs)
print("Total Number of DEGs")
print(v1)

output_table2 <- output_table %>% 
                 mutate(Data_Frame = str_replace_all(Data_Frame, "CACPR_Only_", "")) %>%
                 arrange(desc(Number_of_Obs)) %>%
                 mutate(Data_Frame = factor(Data_Frame, levels = unique(Data_Frame)))
                




p1 <- ggplot(output_table2, aes(x = Data_Frame)) +
  geom_bar(aes(y = Number_of_Positive_Log2FC), stat = "identity", fill = "coral2") +
  geom_bar(aes(y = -Number_of_Negative_Log2FC), stat = "identity", fill = "dodgerblue2") +
  labs(x = "Cell Type", y = "Number of DEGs") +
  ggtitle("CACPR Cell Type DEGs") +
  scale_y_continuous(labels = function(x) abs(x)) +
  annotate("text", x = Inf, y = Inf, label = "Positive Log2FC", color = "coral2",
           hjust = 1, vjust = 1, size = 8) +
  annotate("text", x = Inf, y = Inf, label = "Negative Log2FC", color = "dodgerblue2",
           hjust = 1, vjust = 2.1, size = 8) +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 24),
        axis.text = element_text(color = "black", size = 14,),
        axis.text.x = element_text(color = "black", size = 14, angle = 45, hjust = 1, vjust = 1),
        axis.title = element_text(color = "black", size = 20,))

p1

#rm(list = ls())

```


## Fig 3b and 3c

## Unique 3 Enriched and Depleted CACPR genes by "class" **CACPR Only Object**

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

load(here("Output", "CACPR_Only_Class_Condition_DEGs.RData"))

allobj <- ls()
alldf <- sapply(allobj, get, simplify = FALSE)

alldf <- alldf[c("CACPR_Only_PT", "CACPR_Only_DTL", "CACPR_Only_TAL", "CACPR_Only_DCT", "CACPR_Only_CNT", "CACPR_Only_PC", "CACPR_Only_ICA", "CACPR_Only_ICB", "CACPR_Only_URO", "CACPR_Only_PEC", "CACPR_Only_FIB", "CACPR_Only_CONTRACT", "CACPR_Only_PODO", "CACPR_Only_EC", "CACPR_Only_IMMUNE")]


# Create Enriched Gene List

genelistup <- lapply(alldf,function(i) i[1:100, c(1)]) %>% data.frame
genelistup <- genelistup %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistup <- unlist(genelistup$value)


# Create Depleted Gene List. 

genelistdown <- lapply(alldf,function(i) i[order(i[,"avg_log2FC"], decreasing = FALSE),])
genelistdown <- lapply(genelistdown,function(i) i[1:100, c(1)]) %>% data.frame
genelistdown <- genelistdown %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistdown<- unlist(genelistdown$value)


CACPR <- readRDS(here("Output", "CACPR_integrated.rds"))
DefaultAssay(CACPR) <- "RNA"
Idents(CACPR) <- CACPR@meta.data$subclass.CACPR
SO <- CACPR

SO@meta.data$subclass.CACPR <- factor(SO@meta.data$subclass.CACPR, levels = c("PTS1", "PTS2", "PTS3", "PTinj", "DTL", "TAL1", "TAL2", "MD", "DCT1", "DCT2", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "MES", "CONTRACT", "PODO", "EC", "LYMPH", "MACRO", "LYMPHO"))

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "Sham"))

SO@meta.data <- SO@meta.data %>% 
  mutate(class.Names = case_when(
     Sample == "MH1" ~ "CACPR",
     Sample == "MH3" ~ "Sham",
))

SO@meta.data$class.Names <- factor(SO@meta.data$class.Names, levels = c("Sham", "CACPR"))


```

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

Idents(SO) <- CACPR@meta.data$class.CACPR

DotPlot(SO, features = genelistup, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 


```

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

DotPlot(SO, features = genelistdown, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 

```


## For MH: Unique 3 Enriched and Depleted **CACPR** genes for **ALL object**

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

load(here("Output", "CACPR_All_Condition_DEGs.Rdata"))

allobj <- ls()
alldf <- sapply(allobj, get, simplify = FALSE)

alldf <- alldf[c("CACPR_All_PT", "CACPR_All_DTL", "CACPR_All_TAL", "CACPR_All_DCT", "CACPR_All_CNT", "CACPR_All_PC", "CACPR_All_ICA", "CACPR_All_ICB", "CACPR_All_URO", "CACPR_All_PEC", "CACPR_All_FIB", "CACPR_All_PODO", "CACPR_All_EC", "CACPR_All_IMMUNE"
)]

# Create Enriched Gene List

genelistup <- lapply(alldf,function(i) i[1:100, c(1)]) %>% data.frame
genelistup <- genelistup %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistup <- unlist(genelistup$value)
genelistup_cacpr <- genelistup

# Create Depleted Gene List. 

genelistdown <- lapply(alldf,function(i) i[order(i[,"avg_log2FC"], decreasing = FALSE),])
genelistdown <- lapply(genelistdown,function(i) i[1:100, c(1)]) %>% data.frame
genelistdown <- genelistdown %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistdown<- unlist(genelistdown$value)
genelistdown_cacpr <- genelistdown

All <- readRDS(here("Output", "All_integrated.rds"))
DefaultAssay(All) <- "RNA"

Idents(All) <- All@meta.data$class.sample

All2 <- subset(All, idents = c("CACPR Sham", "CACPR"))
All2 

SO <- All2

SO@meta.data$class.All <- factor(SO@meta.data$class.All, levels = c("PT", "DTL", "TAL", "DCT", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "CONTRACT", "PODO", "EC", "IMMUNE"))

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "CACPR"))

SO@meta.data <- SO@meta.data %>% 
  mutate(class.Names = case_when(
     Sample == "MH1" ~ "CACPR",
     Sample == "MH3" ~ "Sham",
))

SO@meta.data$class.Names <- factor(SO@meta.data$class.Names, levels = c("Sham", "CACPR"))

DimPlot(SO, cols = c("#4974A5", "#B81316"))

save(genelistdown_cacpr, file = here("Output", "genelistdown_cacpr.Rdata"))
save(genelistup_cacpr, file = here("Output", "genelistup_cacpr.Rdata"))

```


```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

Idents(SO) <- SO@meta.data$class.All

DotPlot(SO, features = genelistup, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 

```

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

DotPlot(SO, features = genelistdown, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 

```


## For MH:  Unique 3 Enriched and Depleted **IRI** genes by **ALL object**

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

load(here("Output", "IRI_All_Condition_DEGs.Rdata"))

allobj <- ls()
alldf <- sapply(allobj, get, simplify = FALSE)

alldf <- alldf[c("IRI_All_PT", "IRI_All_DTL", "IRI_All_TAL", "IRI_All_DCT", "IRI_All_CNT", "IRI_All_PC", "IRI_All_ICA", "IRI_All_ICB", "IRI_All_URO", "IRI_All_PEC", "IRI_All_FIB", "IRI_All_PODO", "IRI_All_EC", "IRI_All_IMMUNE"
)]


# Create Enriched Gene List

genelistup <- lapply(alldf,function(i) i[1:100, c(1)]) %>% data.frame
genelistup <- genelistup %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistup <- unlist(genelistup$value)
genelistup_iri <- genelistup

# Create Depleted Gene List. 

genelistdown <- lapply(alldf,function(i) i[order(i[,"avg_log2FC"], decreasing = FALSE),])
genelistdown <- lapply(genelistdown,function(i) i[1:100, c(1)]) %>% data.frame
genelistdown <- genelistdown %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistdown<- unlist(genelistdown$value)
genelistdown_iri <- genelistdown

All <- readRDS(here("Output", "All_integrated.rds"))
DefaultAssay(All) <- "RNA"

Idents(All) <- All@meta.data$class.sample

All2 <- subset(All, idents = c("IRI Sham", "IRI"))
All2 

SO <- All2

SO@meta.data$class.All <- factor(SO@meta.data$class.All, levels = c("PT", "DTL", "TAL", "DCT", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "CONTRACT", "PODO", "EC", "IMMUNE"))

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("IRI Sham", "IRI"))

SO@meta.data <- SO@meta.data %>% 
  mutate(class.Names = case_when(
     class.sample == "IRI Sham" ~ "Sham",
     class.sample == "IRI" ~ "IRI",
))

SO@meta.data$class.Names <- factor(SO@meta.data$class.Names, levels = c("Sham", "IRI"))

DimPlot(SO, cols = c("#45B4A6", "#B755B6"))

save(genelistdown_iri, file = here("Output", "genelistdown_iri.Rdata"))
save(genelistup_iri, file = here("Output", "genelistup_iri.Rdata"))

```


```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

Idents(SO) <- SO@meta.data$class.All

DotPlot(SO, features = genelistup, dot.scale = 8, cols = c("#45B4A6", "#B755B6"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "IRI Enriched") 

```

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=9}

DotPlot(SO, features = genelistdown, dot.scale = 8, cols = c("#45B4A6", "#B755B6"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "IRI Enriched") 

```

## Venn Diagram of Top 3 Depleted Genes

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
rm(list = ls())

load(file = here("Output", "genelistdown_cacpr.Rdata"))
load( file = here("Output", "genelistdown_iri.Rdata"))

set1 <- genelistdown_cacpr
set2 <- genelistdown_iri

venn <- ggvenn(list(CACPR = set1, IRI = set2), text_size = 10, fill_color = c("#B81316", "#B755B6"))
print(venn)

lst <- list(set1, set2)
ItemsList <- venn(lst, show.plot = FALSE)
test <- attributes(ItemsList)$intersections

head(test$A, 20)
head(test$B, 20)
head(test$'A:B', 20)
```

## Venn Diagram of Top 3 Enriched Genes

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}
rm(list = ls())

load(file = here("Output", "genelistup_cacpr.Rdata"))
load( file = here("Output", "genelistup_iri.Rdata"))

set1 <- genelistup_cacpr
set2 <- genelistup_iri

venn <- ggvenn(list(CACPR = set1, IRI = set2), text_size = 10, fill_color = c("#B81316", "#B755B6"))
print(venn)

lst <- list(set1, set2)
ItemsList <- venn(lst, show.plot = FALSE)
test <- attributes(ItemsList)$intersections

head(test$A, 20)
head(test$B, 20)
head(test$'A:B', 20)
```

## For KGB: Unique 3 Enriched and Depleted CACPR genes by **"subclass"** 

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

load(here("Output", "CACPR_Only_Subclass_Condition_DEGs.RData"))

allobj <- ls()
alldf <- sapply(allobj, get, simplify = FALSE)

alldf <- alldf[c("CACPR_Only_PTS1", "CACPR_Only_PTS2", "CACPR_Only_PTS3", "CACPR_Only_PTinj", "CACPR_Only_DTL", "CACPR_Only_TAL1", "CACPR_Only_TAL2", "CACPR_Only_MD", "CACPR_Only_DCT1", "CACPR_Only_DCT2", "CACPR_Only_CNT", "CACPR_Only_PC", "CACPR_Only_ICA", "CACPR_Only_ICB", "CACPR_Only_URO", "CACPR_Only_PEC", "CACPR_Only_FIB", "CACPR_Only_MES", "CACPR_Only_CONTRACT", "CACPR_Only_PODO", "CACPR_Only_EC", "CACPR_Only_LYMPH", "CACPR_Only_MACRO", "CACPR_Only_LYMPHO"
)]


# Create Enriched Gene List

genelistup <- lapply(alldf,function(i) i[1:100, c(1)]) %>% data.frame
genelistup <- genelistup %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistup <- unlist(genelistup$value)


# Create Depleted Gene List. 

genelistdown <- lapply(alldf,function(i) i[order(i[,"avg_log2FC"], decreasing = FALSE),])
genelistdown <- lapply(genelistdown,function(i) i[1:100, c(1)]) %>% data.frame
genelistdown <- genelistdown %>% tidyr::gather() %>% distinct(value, .keep_all = T) %>% group_by(key) %>% filter(row_number()== c(1,2,3))
genelistdown<- unlist(genelistdown$value)



CACPR <- readRDS(here("Output", "CACPR_integrated.rds"))
DefaultAssay(CACPR) <- "RNA"
Idents(CACPR) <- CACPR@meta.data$subclass.CACPR
SO <- CACPR

SO@meta.data$subclass.CACPR <- factor(SO@meta.data$subclass.CACPR, levels = c("PTS1", "PTS2", "PTS3", "PTinj", "DTL", "TAL1", "TAL2", "MD", "DCT1", "DCT2", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "MES", "CONTRACT", "PODO", "EC", "LYMPH", "MACRO", "LYMPHO"))

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "Sham"))

SO@meta.data <- SO@meta.data %>% 
  mutate(class.Names = case_when(
     Sample == "MH1" ~ "CACPR",
     Sample == "MH3" ~ "Sham",
))

SO@meta.data$class.Names <- factor(SO@meta.data$class.Names, levels = c("Sham", "CACPR"))

```


```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}

DotPlot(SO, features = genelistup, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 

```

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}

DotPlot(SO, features = genelistdown, dot.scale = 8, cols = c("#4974A5", "#B81316"), split.by = "class.Names") +  RotatedAxis() + xlab(label = "") + ylab(label = "CACPR Enriched") 

```


# Session Info

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

sessionInfo()

```


  