---
title: "Figure 6 and 7"
author: "Jonathan Nelson and Annie Lackey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
    number_sections: yes
    theme: bootstrap
    df_print: paged
    code_folding: hide
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
if (!require("Seurat")) {install.packages("Seurat"); require("Seurat")}
if (!require("patchwork")) {install.packages("patchwork"); require("patchwork")}
if (!require("knitr")) {install.packages("knitr"); require("knitr")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("BiocManager")) {install.packages("BiocManager"); require("BiocManager")}
if (!require("tibble")) {install.packages("tibble"); require("tibble")}
if (!require("ggpmisc")) {install.packages("ggpmisc"); require("ggpmisc")}
if (!require("RColorBrewer")) {install.packages("RColorBrewer"); require("RColorBrewer")} #color
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")}
if (!require("DESeq2")) {BiocManager::install('DESeq2'); require("DESeq2")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("stringr")) {install.packages("stringr"); require("stringr")}
if (!require("car")) {install.packages("car"); require("car")}
if (!require("openxlsx")) {install.packages("openxlsx"); require("openxlsx")}
if (!require("readxl")) {install.packages("readxl"); require("readxl")}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggvenn")) {install.packages("ggvenn"); require("ggvenn")}
if (!require("kableExtra")) {install.packages("kableExtra"); require("kableExtra")} # for color brewer
if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
if (!require("tidyr")) {install.packages("tidyr"); require("tidyr")}
if (!require("clusterProfiler")) {BiocManager::install('clusterProfiler'); require("clusterProfiler")}
if (!require("enrichplot")) {BiocManager::install('enrichplot'); require("enrichplot")}
if (!require("gplots")) {install.packages("gplots"); require("gplots")}
if (!require("geneName")) {install.packages("geneName"); require("geneName")}




```


# Load PT Dataset

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}
rm(list = ls())

All <- readRDS(here("Output", "All_PT.rds"))
DefaultAssay(All) <- "RNA"

head(All@meta.data)

Idents(All) <- All@meta.data$subclass.PT

DimPlot(All, reduction = "umap")

DimPlot(All, group.by = "class.sample", cols = c("#4974A5", "#B81316", "#45B4A6", "#B755B6"))

DimPlot(All, split.by = "class.sample", label = TRUE)

table(Idents(All))
prop.table(table(Idents(All)))

SO <- All

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "CACPR", "IRI Sham", "IRI"))


```


# Set the color palette

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=12, fig.height=8}

custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

```


# Fig 6

## Fig 6a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1) + ggtitle(NULL) + xlab("UMAP 1") + ylab("UMAP 2") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))


```

## Fig 6b 

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

markers.to.plot.PT <- c("Ccl2",        # PEC
                      "Sema5a",        # Lymph
                      "Dcdc2a",         # Endo
                      "Vcam1",         # Glom Endo
                       "Myc",       # Mesangial
                      "Top2a",        # Mural
                      "Hspa1a",          # Capillary Endo
                      "Krt20",       # Perivascular
                      "Havcr1",       # Fib
                      "Slc16a9",        # B/T Cells 
                      "Slc13a3",        # Uro
                      "Slc5a12",
                      "Lrp2" 
                      )


DotPlot(SO,
features = markers.to.plot.PT,
dot.scale = 8,
dot.min = 0,
scale.max = 100,
scale.min = 0,
col.min = -2.5,
col.max = 2.5) +
  coord_flip() +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab(NULL) +
  ylab(NULL)

# Make the X axis labels at 45 degree

```
# Supplemental Fig 5

## Supplemental Fig 5a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=30, fig.height=20}

f5 <- FeaturePlot(SO,
             features = markers.to.plot.PT,
             cols = c("lightgrey", "royal blue"),
             combine = F, 
             order = T) 

for(i in 1:length(f5)) {
  f5[[i]] <- f5[[i]] & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))
}

cowplot::plot_grid(plotlist = f5)

```

## Supplemental Fig 5b

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width = 8}

t1 <- table(SO@meta.data$subclass.PT, SO@meta.data$class.sample)[, c("CACPR Sham", "CACPR", "IRI Sham", "IRI")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

## Fig 6c

### All Nuclei

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}

Idents(SO) <- SO@meta.data$subclass.PT

DimPlot(SO, reduction = "umap", split.by = "class.sample") & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")



```

### Downsampled to have equal number of nulcei

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

Idents(SO) <- SO@meta.data$class.sample
SO

SO2 <- subset(SO, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 1894)
SO2 

Idents(SO2) <- SO2@meta.data$subclass.PT

DimPlot(SO2, reduction = "umap", split.by = "class.sample", pt.size = 1) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```

## Fig 6d

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

FeaturePlot(SO2, "Lrp2", split.by = "class.sample", pt.size = 1, order = TRUE) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```

## Fig 6e

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

FeaturePlot(SO2, "Havcr1", split.by = "class.sample", pt.size = 1, order = TRUE) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```

## Fig 6f

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=5}

FeaturePlot(SO2, "Hspa1a", split.by = "class.sample", pt.size = 1, order = TRUE) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```




# Fig 7

## GSEA with Ribo Genes

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

load(here("Output", "PT_GSEA.RData"))

```

### Fig 7a CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

p1 <- dotplot(rawGSEA_CACPR_All_PT, showCategory=10, split=".sign") + facet_grid(.~.sign) + labs(title = paste("CACPR")) +        
        theme(plot.title = element_text(hjust = 0.5))

print (p1)

```

### Fig 7b IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

p1 <- dotplot(rawGSEA_IRI_All_PT, showCategory=10, split=".sign") + facet_grid(.~.sign) + labs(title = paste("IRI")) +        
        theme(plot.title = element_text(hjust = 0.5))

print (p1)

```

### Fig 7c Venn

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

set1 <- GSEA_CACPR_All_PT$GO_Description
set2 <- GSEA_IRI_All_PT$GO_Description

venn <- ggvenn(list(CACPR = set1, IRI = set2), text_size = 10, fill_color = c("#B81316", "#B755B6"))
print(venn)


lst <- list(set1, set2)
ItemsList <- venn(lst, show.plot = TRUE)

test <- attributes(ItemsList)$intersections


head(test$A, 20)
head(test$B, 20)
head(test$'A:B', 20)

# create a dataframe from test$A, test$B, test$'A:B'

df <- data.frame(
  CACPR = head(test$A, 10),
  Shared = head(test$'A:B', 10),
  IRI = head(test$B, 10)
)

df

```

## GSEA **without** Ribo Genes

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

load(here("Output", "PT_GSEA_noRibo.RData"))

```

### Fig 7a CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

p1 <- dotplot(rawGSEA_CACPR_All_PT, showCategory=10, split=".sign") + facet_grid(.~.sign) + labs(title = paste("CACPR")) +        
        theme(plot.title = element_text(hjust = 0.5))

print (p1)

```

### Fig 7b IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

p1 <- dotplot(rawGSEA_IRI_All_PT, showCategory=10, split=".sign") + facet_grid(.~.sign) + labs(title = paste("IRI")) +        
        theme(plot.title = element_text(hjust = 0.5))

print (p1)

```

### Fig 7b Venn

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

set1 <- GSEA_CACPR_All_PT$GO_Description
set2 <- GSEA_IRI_All_PT$GO_Description

venn <- ggvenn(list(CACPR = set1, IRI = set2), text_size = 10, fill_color = c("#B81316", "#B755B6"))
print(venn)


lst <- list(set1, set2)
ItemsList <- venn(lst, show.plot = TRUE)

test <- attributes(ItemsList)$intersections


head(test$A, 20)
head(test$B, 20)
head(test$'A:B', 20)

# create a dataframe from test$A, test$B, test$'A:B'

df <- data.frame(
  CACPR = head(test$A, 10),
  Shared = head(test$'A:B', 10),
  IRI = head(test$B, 10)
)

df

?ggvenn

```

## Fig 7 KPMP AKI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

rm(list = ls())

load(here("Output", "KPMP.AKIintegrated.PT2.RData"))

load(here("Output", "CACPR_All_Condition_DEGs.Rdata"))
load(here("Output", "IRI_All_Condition_DEGs.Rdata"))

```


### Fig 7 KPMP AKI vs. CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

x.markers <- CACPR_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- DEGs
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
x.markers_tb_H <- mousegnameConverter(x.markers_tb, "gene")

    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb_H, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "CACPR", "and",
                      "KPPMP AKI", sep = " "), 
        x = paste("Average log2FC", "CACPR"), 
        y = paste("Average log2FC ", "KPMP")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)
    
    print(nrow(xy.comp))
    
results <- cor.test(xy.comp$avg_log2FC.x, xy.comp$avg_log2FC.y)

results

```

### Fig 7 KPMP AKI vs. IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

x.markers <- IRI_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- DEGs
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
x.markers_tb_H <- mousegnameConverter(x.markers_tb, "gene")

    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb_H, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "IRI", "and", "KPMP AKI"
                      , sep = " "), 
        x = paste("Average log2FC", "IRI"), 
        y = paste("Average log2FC ", "KPMP")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)
    
    print(nrow(xy.comp))
    
results <- cor.test(xy.comp$avg_log2FC.x, xy.comp$avg_log2FC.y)

results

```


# Supplemental Fig 6

### KPMP CKD Correlation

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=10, fig.width=10}

rm(list = ls())

load(here("Output", "KPMP.CKDintegrated.PT2.RData"))

load(here("Output", "CACPR_All_Condition_DEGs.Rdata"))
load(here("Output", "IRI_All_Condition_DEGs.Rdata"))

```

### Fig S6a KPMP CKD vs. CACPR

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

x.markers <- CACPR_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- DEGs
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
x.markers_tb_H <- mousegnameConverter(x.markers_tb, "gene")

    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb_H, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "CACPR", "and",
                      "KPMP CKD", sep = " "), 
        x = paste("Average log2FC", "CACPR"), 
        y = paste("Average log2FC ", "KPMP")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)
    
    print(nrow(xy.comp))
    
```

### Fig S6b KPMP CKD vs. IRI

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

x.markers <- IRI_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- DEGs
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
x.markers_tb_H <- mousegnameConverter(x.markers_tb, "gene")

    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb_H, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "IRI", "and",
                      "KPMP CKD", sep = " "), 
        x = paste("Average log2FC", "IRI"), 
        y = paste("Average log2FC ", "KPMP")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)
    
    print(nrow(xy.comp))

```

# Bonus Ribosome Story

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}

All <- readRDS(here("Output", "All_PT.rds"))
SO <- All
Idents(SO) <- SO@meta.data$class.sample
SO
SO2 <- subset(SO, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 1894)



FeaturePlot(SO2, "percent.ribo", split.by = "class.sample", pt.size = 1, order = TRUE, max.cutoff = 5) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```



```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO2, "percent.ribo", split.by = "class.sample", y.max = 5)

```

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}

FeaturePlot(SO2, "percent.mt", split.by = "class.sample", pt.size = 1, order = TRUE, max.cutoff = 5) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO2, "percent.mt", split.by = "class.sample", y.max = 5)

```

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

FeatureScatter(SO2, feature1 = "percent.ribo", feature2 = "percent.mt", pt.size = 1, group.by = "class.lab") & xlab("Ribosome") & ylab("Mitochondria") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```

# Session Info

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

sessionInfo()

```


  