---
title: "Figure 4 and 5"
author: "Jonathan Nelson and Annie Lackey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: yes
    toc_depth: 3
    toc_float: true
    number_sections: yes
    theme: bootstrap
    df_print: paged
    code_folding: hide
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load new packages, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
if (!require("Seurat")) {install.packages("Seurat"); require("Seurat")}
if (!require("patchwork")) {install.packages("patchwork"); require("patchwork")}
if (!require("knitr")) {install.packages("knitr"); require("knitr")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("BiocManager")) {install.packages("BiocManager"); require("BiocManager")}
if (!require("tibble")) {install.packages("tibble"); require("tibble")}
if (!require("ggpmisc")) {install.packages("ggpmisc"); require("ggpmisc")}
if (!require("RColorBrewer")) {install.packages("RColorBrewer"); require("RColorBrewer")} #color
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")}
if (!require("DESeq2")) {BiocManager::install('DESeq2'); require("DESeq2")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("stringr")) {install.packages("stringr"); require("stringr")}
if (!require("car")) {install.packages("car"); require("car")}
if (!require("openxlsx")) {install.packages("openxlsx"); require("openxlsx")}
if (!require("readxl")) {install.packages("readxl"); require("readxl")}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggvenn")) {install.packages("ggvenn"); require("ggvenn")}
if (!require("kableExtra")) {install.packages("kableExtra"); require("kableExtra")} # for color brewer
if (!require("corrplot")) {install.packages("corrplot"); require("corrplot")}
if (!require("tidyr")) {install.packages("tidyr"); require("tidyr")}

```


# Load All Dataset

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}
rm(list = ls())

All <- readRDS(here("Output", "All_integrated.rds"))
DefaultAssay(All) <- "RNA"

head(All@meta.data)

Idents(All) <- All@meta.data$subclass.All

DimPlot(All, reduction = "umap")

DimPlot(All, group.by = "class.sample", cols = c("#4974A5", "#B81316", "#45B4A6", "#B755B6"))

DimPlot(All, split.by = "class.sample", label = TRUE)

table(Idents(All))
prop.table(table(Idents(All)))

SO <- All

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "CACPR", "IRI Sham", "IRI"))

SO@meta.data$subclass.All <- factor(SO@meta.data$subclass.All, levels = c("PTS1", "PTS2", "PTS3", "PTinj", "DTL", "TAL1", "TAL2", "DCT1", "DCT2", "CNT", "PC", "ICA", "ICB", "URO", "PEC", "FIB", "MES", "PODO", "EC", "IMMUNE"))

```

# Set the color palette

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

```



# Fig 4

## Fig 4a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1) + ggtitle(NULL) + xlab("UMAP 1") + ylab("UMAP 2") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))


```

## Fig 4b 

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=10}

markers.to.plot1 <- c("Lrp2",         # PT
                      "Slc5a12",      # PT-S1
                      "Slc13a3",      # PT-S2
                      "Slc16a9",      # PT-S3
                      "Havcr1",       # Injured PT
                      "Epha7",        # dTL
                      "Slc12a1",      # TAL
                      "Cldn10",       # TAL
                      "Cldn16",       # TAL
                      "Slc12a3",      # DCT
                      "Pvalb",        # DCT1
                      "Slc8a1",       # DCT2, CNT
                      "Aqp2",         # PC
                      "Slc4a1",       # IC-A
                      "Slc26a4",      # IC-B
                      "Upk1b",        # Uro
                      "Ncam1",        # PEC
                      "Pdgfrb",       # Perivascular
                      "Piezo2",       # Mesangial
                      "Pdgfra",       # Fib
                      "Acta2",        # Mural
                      "Nphs1",        # Podo
                      "Kdr",          # Capillary Endo
                      "Ptprc"        # Immune
                      )


DotPlot(SO,
features = markers.to.plot1,
dot.scale = 8,
dot.min = 0,
scale.max = 100,
scale.min = 0,
col.min = -2.5,
col.max = 2.5) +
  coord_flip() +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab(NULL) +
  ylab(NULL)


```

# Supplemental Fig 3

## Fig S3a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

SO@meta.data$class.lab <- factor(SO@meta.data$class.lab , levels = c("Hutchens", "Humphreys"))

VlnPlot(SO, "nFeature_RNA", split.by = "class.sample", group.by = "class.lab", pt.size = 0.1) +
  theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  ylab("Number of Genes Detected") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("nFeature RNA")


```

## Fig S3b

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO, "nCount_RNA", split.by = "class.sample", group.by = "class.lab", pt.size = 0.1) +
    theme_classic() +
  theme(
    axis.line = element_line(size = 1, colour = "black"),
    text = element_text(size = 20),
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) +
  ylab("Number of mRNA Molecules Detected") +
  scale_fill_manual(values = custom_colors) +
  ggtitle("nCount RNA")


table(SO@meta.data$class.sample)

df <- FetchData(object = SO, vars = c("class.sample", "class.lab", "nFeature_RNA", "nCount_RNA"), layer = "counts")

df2 <- df %>%
  group_by(class.sample) %>%
  summarize(
    Count = n(),
    "Median nFeature_RNA" = median(nFeature_RNA, na.rm = TRUE),
    "Median nCount_RNA" = median(nCount_RNA, na.rm = TRUE)
  ) %>%
  as.data.frame()

df2

df3 <- df %>%
  group_by(class.lab) %>%
  summarize(
    Count = n(),
    "Median nFeature_RNA" = median(nFeature_RNA, na.rm = TRUE),
    "Median nCount_RNA" = median(nCount_RNA, na.rm = TRUE)
  ) %>%
  as.data.frame()

df3


```

## Fig S2c


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=30, fig.height=20}

f5 <- FeaturePlot(SO,
             features = markers.to.plot1,
             cols = c("lightgrey", "royal blue"),
             combine = F, 
             order = T) 

for(i in 1:length(f5)) {
  f5[[i]] <- f5[[i]] & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))
}

cowplot::plot_grid(plotlist = f5)

```



```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=12, fig.height=8}

DimPlot(SO, reduction = "umap", pt.size = 1, label = TRUE, label.size = 6, repel = TRUE) + ggtitle(NULL) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))

```


## Fig 4c

### All Nuclei

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=20, fig.height=6}

Idents(SO) <- SO@meta.data$subclass.All

DimPlot(SO, reduction = "umap", split.by = "class.sample", pt.size = 1) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```

### Downsampled to have equal numbers of nuclei

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}

Idents(SO) <- SO@meta.data$class.sample
SO

SO2 <- subset(SO, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)
SO2 

Idents(SO2) <- SO2@meta.data$subclass.All

DimPlot(SO2, reduction = "umap", split.by = "class.sample", pt.size = 1) & xlab("UMAP 1") & ylab("UMAP 2") + theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```

# Supplemental Fig 4

## Supplemental 4a

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10, fig.height=8}

DimPlot(SO2, reduction = "umap", pt.size = 1, group.by = "class.sample", cols = c("#4974A5", "#B81316", "#45B4A6", "#B755B6")) & xlab("UMAP 1") & ylab("UMAP 2") + theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20))

```



## Supplemental 4b: Proportion by "subclass"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width = 8}

t1 <- table(SO@meta.data$subclass.All, SO@meta.data$class.sample)[, c("CACPR Sham", "CACPR", "IRI Sham", "IRI")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

## Supplemental 4c: Proportion by "class"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width = 8}

t1 <- table(SO@meta.data$class.All, SO@meta.data$class.sample)[, c("CACPR Sham", "CACPR", "IRI Sham", "IRI")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```

## Supplemental 4d: Proportion by "type"

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width = 8}

t1 <- table(SO@meta.data$type.All, SO@meta.data$class.sample)[, c("CACPR Sham", "CACPR", "IRI Sham", "IRI")]
t1

prop.t1 <- prop.table(t1, margin = 2) 
prop.t1

t2 <- as.data.frame(t1)
colnames(t2) <- c('Cell_type', 'Experimental_Group', 'Frequency')

# Original plot

ggplot(t2, aes(fill=Cell_type, y=Frequency, x=Experimental_Group)) + 
  geom_bar(position="fill", stat = "identity", fun.y = "mean", colour="black") +
  theme_classic() +
  theme(axis.line = element_line(size = 1, colour = "black"),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        text = element_text(size=20)) +
  labs(fill = "Cell Type") +
  xlab(NULL)

```


## Supplemental 4e: DEG numbers by CACPR


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

rm(list = ls())

load(here("Output", "CACPR_All_Condition_DEGs.RData"))

# List the objects in the environment
  objects_in_environment <- ls()

data_frames <- Filter(is.data.frame, mget(ls()))

# Initialize an empty data frame to store the results
output_table <- data.frame(Data_Frame = character(),
                           Number_of_Obs = numeric(),
                           Number_of_Positive_Log2FC = numeric(),
                           Number_of_Negative_Log2FC = numeric(),
                           stringsAsFactors = FALSE)

# Loop through each data frame
for (df_name in names(data_frames)) {
  df <- data_frames[[df_name]]
  
  # Get the number of observations in the data frame
  num_obs <- nrow(df)
  
  # Count the number of observations with positive log2FC
  positive_count <- sum(df$avg_log2FC > 0)
  
  # Count the number of observations with negative log2FC
  negative_count <- sum(df$avg_log2FC < 0)
  
  # Create a row in the output table
  output_row <- data.frame(Data_Frame = df_name,
                           Number_of_Obs = num_obs,
                           Number_of_Positive_Log2FC = positive_count,
                           Number_of_Negative_Log2FC = negative_count,
                           stringsAsFactors = FALSE)
  
  # Append the row to the output table
  output_table <- rbind(output_table, output_row)
}

# Print the output table
output_table

```

### Print Graph of DEGs

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=6, fig.width=10}

# Measure the total number of DEGs (sum of output_table$Number_of_Obs)
v1 <-sum(output_table$Number_of_Obs)
print("Total Number of DEGs")
print(v1)

output_table2 <- output_table %>% 
                 mutate(Data_Frame = str_replace_all(Data_Frame, "CACPR_All_", "")) %>%
                 arrange(desc(Number_of_Obs)) %>%
                 mutate(Data_Frame = factor(Data_Frame, levels = unique(Data_Frame)))
                




p1 <- ggplot(output_table2, aes(x = Data_Frame)) +
  geom_bar(aes(y = Number_of_Positive_Log2FC), stat = "identity", fill = "coral2") +
  geom_bar(aes(y = -Number_of_Negative_Log2FC), stat = "identity", fill = "dodgerblue2") +
  labs(x = "Cell Type", y = "Number of DEGs") +
  ggtitle("CACPR Cell Type DEGs") +
  scale_y_continuous(labels = function(x) abs(x)) +
  annotate("text", x = Inf, y = Inf, label = "Positive Log2FC", color = "coral2",
           hjust = 1, vjust = 1, size = 8) +
  annotate("text", x = Inf, y = Inf, label = "Negative Log2FC", color = "dodgerblue2",
           hjust = 1, vjust = 2.1, size = 8) +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 24),
        axis.text = element_text(color = "black", size = 14,),
        axis.text.x = element_text(color = "black", size = 14, angle = 45, hjust = 1, vjust = 1),
        axis.title = element_text(color = "black", size = 20,))

p1

#rm(list = ls())
```


## Supplemental 4e: DEG numbers by IRI

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

rm(list = ls())

load(here("Output", "IRI_All_Condition_DEGs.RData"))

# List the objects in the environment
  objects_in_environment <- ls()

data_frames <- Filter(is.data.frame, mget(ls()))

# Initialize an empty data frame to store the results
output_table <- data.frame(Data_Frame = character(),
                           Number_of_Obs = numeric(),
                           Number_of_Positive_Log2FC = numeric(),
                           Number_of_Negative_Log2FC = numeric(),
                           stringsAsFactors = FALSE)

# Loop through each data frame
for (df_name in names(data_frames)) {
  df <- data_frames[[df_name]]
  
  # Get the number of observations in the data frame
  num_obs <- nrow(df)
  
  # Count the number of observations with positive log2FC
  positive_count <- sum(df$avg_log2FC > 0)
  
  # Count the number of observations with negative log2FC
  negative_count <- sum(df$avg_log2FC < 0)
  
  # Create a row in the output table
  output_row <- data.frame(Data_Frame = df_name,
                           Number_of_Obs = num_obs,
                           Number_of_Positive_Log2FC = positive_count,
                           Number_of_Negative_Log2FC = negative_count,
                           stringsAsFactors = FALSE)
  
  # Append the row to the output table
  output_table <- rbind(output_table, output_row)
}

# Print the output table
output_table

```

### Print Graph of DEGs

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.height=6, fig.width=10}

# Measure the total number of DEGs (sum of output_table$Number_of_Obs)
v1 <-sum(output_table$Number_of_Obs)
print("Total Number of DEGs")
print(v1)

output_table2 <- output_table %>% 
                 mutate(Data_Frame = str_replace_all(Data_Frame, "IRI_All_", "")) %>%
                 arrange(desc(Number_of_Obs)) %>%
                 mutate(Data_Frame = factor(Data_Frame, levels = unique(Data_Frame)))
                




p1 <- ggplot(output_table2, aes(x = Data_Frame)) +
  geom_bar(aes(y = Number_of_Positive_Log2FC), stat = "identity", fill = "coral2") +
  geom_bar(aes(y = -Number_of_Negative_Log2FC), stat = "identity", fill = "dodgerblue2") +
  labs(x = "Cell Type", y = "Number of DEGs") +
  ggtitle("IRI Cell Type DEGs") +
  scale_y_continuous(labels = function(x) abs(x)) +
  annotate("text", x = Inf, y = Inf, label = "Positive Log2FC", color = "coral2",
           hjust = 1, vjust = 1, size = 8) +
  annotate("text", x = Inf, y = Inf, label = "Negative Log2FC", color = "dodgerblue2",
           hjust = 1, vjust = 2.1, size = 8) +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 24),
        axis.text = element_text(color = "black", size = 14,),
        axis.text.x = element_text(color = "black", size = 14, angle = 45, hjust = 1, vjust = 1),
        axis.title = element_text(color = "black", size = 20,))

p1

rm(list = ls())
```

## Fig 4d

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}


All <- readRDS(here("Output", "All_integrated.rds"))
DefaultAssay(All) <- "RNA"
SO <- All
Idents(SO) <- SO@meta.data$class.sample
SO

SO2 <- subset(SO, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)


FeaturePlot(SO2, "Havcr1", split.by = "class.sample", pt.size = 1, order = TRUE) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")


```

## Fig 4f

### Set the color palette

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

```


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE,  fig.width=6, fig.height=6}

Idents(SO) <- "class.All"

SO@meta.data$class.sample <- factor(SO@meta.data$class.sample, levels = c("CACPR Sham", "CACPR", "IRI Sham", "IRI"))

VlnPlot(SO, features = "Havcr1", idents = "PT", group.by = "class.All", split.by = "class.sample", pt.size = 1,) +
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
        axis.text.x = element_blank()
      ) + xlab("") +
  scale_fill_manual(values = custom_colors)


```

# Fig 5

## Fig 5a: Cluster Correlation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

rsq_table <- read.csv(here("Output", "R2_for_IRI_Vs_CACPR_Cluster_DEGs_NO_FILTER_2024.csv"))


df <- rsq_table %>%
                dplyr::select(CACPR, IRI, "R.squared")  %>%
                mutate(CACPR = sub(".*\\.", "", CACPR)) %>%
                mutate(IRI = sub(".*\\.", "", IRI)) %>%
                pivot_wider(names_from = IRI, values_from = "R.squared") %>%
                column_to_rownames(var = "CACPR") %>%
                as.matrix()

rownames(df) <- sub("^CACPR_All_", "", rownames(df))
colnames(df) <- sub("^IRI_All_", "", colnames(df))

corrplot(df, method = 'color', tl.col = 'black')

extract_suffix <- function(string) {
  parts <- str_split(string, "_")[[1]]
  if (length(parts) > 2) {
    return(parts[3])
  } else {
    return(NA)
  }
}

rsq_table2 <- rsq_table %>%
  mutate(
    CACPR_suffix = sapply(CACPR, extract_suffix),
    IRI_suffix = sapply(IRI, extract_suffix),
    Same_Ending = if_else(CACPR_suffix == IRI_suffix, TRUE, FALSE)
  ) %>%
  select(-CACPR_suffix, -IRI_suffix) 

df4 <- rsq_table2 %>%
  group_by(Same_Ending) %>%
  summarize(
    "Mean R2" = mean(R.squared, na.rm = TRUE),
    SEM = sd(R.squared, na.rm = TRUE) / sqrt(n())
  ) %>%
  as.data.frame()

df4

```

## Fig 5b: Cluster Correlation Example (PT)

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

load(here("Output", "CACPR_All_Cluster_DEGs.Rdata"))
load(here("Output", "IRI_All_Cluster_DEGs.Rdata"))

  x.markers <- CACPR_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- IRI_All_PT
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "CACPR", "and",
                      "IRI", sep = " "), 
        x = paste("Average log2FC", "CACPR"), 
        y = paste("Average log2FC ", "IRI")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)




```

## Fig 5c: Condition Correlation

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

rm(list = ls())

rsq_table <- read.csv(here("Output", "R2_for_IRI_Vs_CACPR_Condition_DEGs_No_Filter.csv"))


df <- rsq_table %>%
                dplyr::select(CACPR, IRI, "R.squared") %>%
                mutate(CACPR = sub(".*\\.", "", CACPR)) %>%
                mutate(IRI = sub(".*\\.", "", IRI)) %>%
                pivot_wider(names_from = IRI, values_from = "R.squared") %>%
                column_to_rownames(var = "CACPR") %>%
                as.matrix()

rownames(df) <- sub("^CACPR_All_", "", rownames(df))
colnames(df) <- sub("^IRI_All_", "", colnames(df))

corrplot(df, method = 'color', tl.col = 'black') 

extract_suffix <- function(string) {
  parts <- str_split(string, "_")[[1]]
  if (length(parts) > 2) {
    return(parts[3])
  } else {
    return(NA)
  }
}

rsq_table2 <- rsq_table %>%
  mutate(
    CACPR_suffix = sapply(CACPR, extract_suffix),
    IRI_suffix = sapply(IRI, extract_suffix),
    Same_Ending = if_else(CACPR_suffix == IRI_suffix, TRUE, FALSE)
  ) %>%
  select(-CACPR_suffix, -IRI_suffix) 

df5 <- rsq_table2 %>%
  group_by(Same_Ending) %>%
  summarize(
    "Mean R2" = mean(R.squared, na.rm = TRUE),
    SEM = sd(R.squared, na.rm = TRUE) / sqrt(n())
  ) %>%
  as.data.frame()

df5


```

## Fig 5d: Condition Correlation Example (PT)

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

rm(list = ls())

load(here("Output", "CACPR_All_Condition_DEGs.Rdata"))
load(here("Output", "IRI_All_Condition_DEGs.Rdata"))

  x.markers <- CACPR_All_PT
  
  #Making “Gene Names” as Column 1
  x.markers_tb <- x.markers %>%
    data.frame() %>% 
    as_tibble()
  
  y.markers <- IRI_All_PT
    
    y.markers_tb <- y.markers %>%
      data.frame() %>%
      as_tibble()
    
    #X-Y DEGs Intersection Table
    
    xy.comp <- inner_join(x.markers_tb, y.markers_tb, by = "gene")
    
    #Set Range for Far Right Data Points
    df.upper <- subset(xy.comp, avg_log2FC.x > -.32 & avg_log2FC.y > -.32)
    #Set Range for Far Left Data Points
    df.lower <- subset(xy.comp, avg_log2FC.x < 0.32 & avg_log2FC.y < .32)
    
    xy.comp.plot <- ggplot(xy.comp, aes(x = avg_log2FC.x, y = avg_log2FC.y, label=gene)) +
      theme_classic() +
      geom_point(
        color=dplyr::case_when(
          (xy.comp$avg_log2FC.x > 1 & xy.comp$avg_log2FC.y > 1) ~ "#1b9e77", #sets color for df.upper points
          (xy.comp$avg_log2FC.x < -1 & xy.comp$avg_log2FC.y < -1) ~ "#d95f02", #sets color for df.lower points
          TRUE ~ "black")) +
      geom_text_repel(data=rbind(df.upper, df.lower),
                      segment.sixy.compe  = 0.2, #<--!! what is this?? !!--
                      segment.color = "grey50") +
      geom_smooth (method=lm) +
      labs(
        title = paste("Correlation of Log2FC Values of DEGs from",
                      "CACPR", "and",
                      "IRI", sep = " "), 
        x = paste("Average log2FC", "CACPR"), 
        y = paste("Average log2FC ", "IRI")
      ) +
      stat_poly_eq(aes(label = paste(..rr.label.., sep = "~~~")),
                   label.x.npc = "left", label.y.npc = 0.90, #set the position of the eq
                   rr.digits = 3)
    
    print(xy.comp.plot)

```

# Bonus: Ribosome Story

```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, fig.width=16, fig.height=6}

All <- readRDS(here("Output", "All_integrated.rds"))
DefaultAssay(All) <- "RNA"
SO <- All
Idents(SO) <- SO@meta.data$class.sample
SO

SO2 <- subset(SO, idents = c("CACPR Sham", "IRI Sham", "CACPR", "IRI"), downsample = 5524)



FeaturePlot(SO2, "percent.ribo", split.by = "class.sample", pt.size = 1, order = TRUE, max.cutoff = 5) & xlab("UMAP 1") & ylab("UMAP 2") +
  theme_classic() &
  theme(axis.line = element_line(size = 1, colour = "black"),
        text = element_text(size=20),
         legend.position = "none")

```

### Set the color palette

```{r echo=TRUE, error=FALSE, message=FALSE, warning=FALSE}

custom_colors <- c(
  "CACPR Sham" = "#4974A5",
  "CACPR" = "#B81316",
  "IRI Sham" = "#45B4A6",
  "IRI" = "#B755B6"
)

```


```{r echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

VlnPlot(SO2, "percent.ribo", group.by = "class.sample", y.max = 5) +
  scale_fill_manual(values = custom_colors) 

```

# Session Info

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}

sessionInfo()

```


  